---
title: "Getting and Cleaning Data Quiz 1"
date: "6 Feb 2015"
output: html_document
---

Data Science Specialization Get Data course.

Quiz 1 

> Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 
```
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv", destfile="./getquiz1.csv")
```
```{r}
data=read.csv("getquiz1.csv")
```
How many properties are worth $1,000,000 or more?
```{r}
sum(!is.na(data$VAL[data$VAL==24]))
```
> Question 2

Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?
```{r}
length(data$FES)
```

> Question 3

Download the Excel spreadsheet on Natural Gas Aquisition Program , and CRAN package xlsx:

```
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx", destfile="./getquiz1.xlsx")

install.packages("xlsx")
library(xlsx)
```
Read rows 18-23 and columns 7-15 into R and assign the result to a variable called 'dat'
```{r}
library(xlsx)
colIndex <- 7:15
rowIndex <- 18:23
dat <- read.xlsx("./getquiz1.xlsx", sheetIndex=1, header=TRUE, colIndex=colIndex, rowIndex=rowIndex)
```
What is the value of:
```{r}
sum(dat$Zip*dat$Ext,na.rm=T)
```

> Question 4

Read the XML data on Baltimore restaurants from here: 
How many restaurants have zipcode 21231?

```{r}
library(XML)
fileUrl <- "http://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
dat <- xmlTreeParse(fileUrl, useInternal=TRUE)
rootNode <- xmlRoot(dat)
sum(xpathSApply(rootNode, "//zipcode", xmlValue)==21231)
```
