---
title: "R Quiz 2"
author: "amk"
date: "15 January 2015"
output: html_document
---


Data Science Specialization R course.

Quiz 12

> Question 1

Suppose I define the following function in R

```{r}
cube <- function(x, n) {
        x^3
}
cube(3)
```

> Question 2

The following code will produce a warning in R.

```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```
Answer

x is an iterable(vector). 'If' Logical operations can only be done on a sigle operand at a time and not the entire interable entity.

> Question 3

Consider the following function

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```
Answer
```{r}
z <- 10
f(3)
```

> Question 4

Consider the following expression:
```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```
Answer
```{r}
y
```

> Question 5

Consider the following R function
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
Answer

f is not defined within the funtion, nor passed as an argumnent to the said function.