---
title: "R Quiz 1"
author: "amk"
date: "13 January 2015"
output: html_document
---

Data Science Specialization R course.

Quiz 1 

INPUT -> Download the zip file form the quiz page and unzip it and import it by the following command

```{r}
data <- read.csv("hw1_data.csv")
```

> Question 11

In the dataset provided for this Quiz, what are the column names of the dataset?

Answer

The column names when tryin to print a row are given as informantio by the console
```{r}
data[1, ]
```

> Question 12

Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

Answer
```{r}
data[1:2,]
```
> Question 13

How many observations (i.e. rows) are in this data frame?

Answer
```{r}
nrow(data)
```

> Question 14

Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

Answer
```{r}
tail(data,2)
```

> Question 15

What is the value of Ozone in the 47th row?

Answer 
```{r}
data[47, "Ozone"]

```

> Question 16

How many missing values are in the Ozone column of this data frame?

Answer
```{r}
sum(is.na(data[,"Ozone"]))
```

> Question 17

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

Answer
```{r}
mean(data$Ozone, na.rm=TRUE)
```

> Question 18

Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

Answer
```{r}
dat <- data[data[, "Ozone"] > 31 & data[, "Temp"] > 90, ]
mean(dat$Solar.R, na.rm=TRUE)
```

> Question 19

What is the mean of "Temp" when "Month" is equal to 6?

Answer
```{r}
dat <- data[data[, "Month"] == 6,]
mean(dat$Temp)
```

> Question 20

What was the maximum ozone value in the month of May (i.e. Month = 5)?

Answer
```{r}
dat <- data[data[,"Month"] == 5, ]
max(dat$Ozone, na.rm=TRUE)
```
